---
output: html_document
editor_options: 
  chunk_output_type: console
---

<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)
library(latex2exp)
library(MASS)
library(plotly)

lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
Germany.dir=here("data/ACC_tests/Germany/")
RLG.dir=here("data/ACC_tests/RLG/")
fig.dir = here("figs/")
output.dir = here("output/")

```

# Germany networks

## Processing Germany network accuracy files

```{r}

## Source supporting functions
Matlab_readin <- path(code.dir, "Matlab_readin.R")
source(Matlab_readin)

########################################################
## LOOP TO COMBINE AND PROCESS ALL ACCURACY FILES

## Inputs -- names and parameters of ACC files
acc_inputs <- matrix(nrow=10, ncol=2)
colnames(acc_inputs) <- c("filename","num_iter")
# acc_inputs[,"filename"] <- c("ACC_SimSig_V10_30_Star_Acc2","ACC_SimSig_V7_30_Star_Acc2","ACC_SimSig_V8_30_Star_Acc2","ACC_SimSig_V9_50_Star_Acc2","ACC_SimSig_V11_30_Star_Acc2")
# acc_inputs[,"filename"] <- c("ACC_raw_V10_30_Star_Acc2","ACC_raw_V7_30_Star_Acc2",
#                             "ACC_raw_V8_30_Star_Acc2","ACC_raw_V9_50_Star_Acc2","ACC_raw_V11_30_Star_Acc2",
#                             "ACC_raw_V12_50_Star_Acc2", "ACC_raw_V13_150_Star_Acc2")
acc_inputs[,"filename"] <- c("ACC_SimSigR_V12_50_Star_Acc2","ACC_SimSigR_V13_150_Star_Acc2","ACC_SimSigR_V14_50_Star_Acc2","ACC_SimSigR_V15_50_Star_Acc2","ACC_SimSigR_V16_50_Star_Acc2","ACC_SimSigR_V17_20_Star_Acc2","ACC_SimSigR_V18_130_Star_Acc2","ACC_SimSigR_V19_50_Star_Acc2","ACC_SimSigR_V20_50_Star_Acc2","ACC_SimSigR_V21_50_Star_Acc2")
#acc_inputs[,"num_iter"] <- c(30, 30, 30, 50, 30, 50, 150)
acc_inputs[,"num_iter"] <- c(50,150,50,50,50,20,130,50,50,50)
nr_obIter <- sum(as.numeric(acc_inputs[,"num_iter"]))
nr_files <- nrow(acc_inputs)

## Initialize dataframes and parameters
ACC1_data_full <- NULL
ACC2_data_full <- NULL
rank_data_full <- NULL
SigStar_data_full <- NULL
SigStarRatio_data_full <- NULL
prev_max_iter = 0

## Loop to combine and process each file 

for (file.idx in 1:nr_files){
  #acc_list_curr <- acc_list[[i]]
  filename <- acc_inputs[file.idx,1]
  num_iter <- as.numeric(acc_inputs[file.idx,2])
  
  ################## Matlab readin
  
  readin_path <- path(Germany.dir, paste0(filename,".csv"))

  acc_data = read.csv(readin_path, sep=",", header=FALSE) # ,stringsAsFactors = FALSE))
  
  ## VARIABLE NAMES
  ill_interval <- c(seq(20,100,by=20), seq(150,300,by=50))
  num_ill_interval <- length(ill_interval)
  #num_iter <- num_iter
  num_nets <- 7
  net_names <- c("vegetables","eggs","meatProducts","cheese","milkProducts","poultry","milk")
 
  ## EXTRACT ACC DATA
  ACC1_data <- t(acc_data[c(1:9),])
  ACC2_data <- t(acc_data[c(11:19),])
  rank_data <- t(acc_data[c(21:29),])
  SigStar_data <- t(acc_data[c(31:39),])
  SigStarRatio_data <- t(acc_data[c(41:49),])
  
  ##################
  
  ACC1_data <- Matlab_format(ACC1_data, num_iter=num_iter, prev_max_iter=prev_max_iter,ill_interval=ill_interval)
  ACC1_data_full <- rbind(ACC1_data, ACC1_data_full)
  
  ACC2_data <- Matlab_format(ACC2_data, num_iter=num_iter, prev_max_iter=prev_max_iter,ill_interval=ill_interval)
  ACC2_data_full <- rbind(ACC2_data, ACC2_data_full)
  
  rank_data <- Matlab_format(rank_data, num_iter=num_iter, prev_max_iter=prev_max_iter,ill_interval=ill_interval)
  rank_data_full <- rbind(rank_data, rank_data_full)
  
  SigStar_data <- Matlab_format(SigStar_data, num_iter=num_iter, prev_max_iter=prev_max_iter,ill_interval=ill_interval)
  SigStar_data_full <- rbind(SigStar_data, SigStar_data_full)
  
  SigStarRatio_data <- Matlab_format(SigStarRatio_data, num_iter=num_iter, prev_max_iter=prev_max_iter,ill_interval=ill_interval)
  SigStarRatio_data_full <- rbind(SigStarRatio_data, SigStarRatio_data_full)
  
  prev_max_iter <- prev_max_iter + num_iter
  
}

## Divide SigStar by SigStarRatio to get SigStarHat
SigStarHat_data_full <- SigStar_data_full
SigStarHat_data_full <- dplyr::rename(SigStarHat_data_full, SigStar=value)
SigStarHat_data_full <- cbind(SigStarHat_data_full, SigStarRatio_data_full$value) %>% dplyr::rename(SigStarHat = "SigStarRatio_data_full$value")
SigStarHat_data_full$value <- SigStarHat_data_full$SigStar / SigStarHat_data_full$SigStarHat

## Get CI overall and for each net, for each accuracy statistic
CI.ACC1_net <- get.CI(ACC1_data_full, by_net=1)
CI.ACC1_all <- get.CI(ACC1_data_full, by_net=0)
CI.ACC2_net <- get.CI(ACC2_data_full, by_net=1)
CI.ACC2_all <- get.CI(ACC2_data_full, by_net=0)
CI.rank_net <- get.CI(rank_data_full, by_net=1)
CI.rank_all <- get.CI(rank_data_full, by_net=0)
CI.SigStar_net <- get.CI(SigStar_data_full, by_net=1)
CI.SigStar_all <- get.CI(SigStar_data_full, by_net=0)
CI.SigStarHat_net <- get.CI(SigStarHat_data_full, by_net=1)
CI.SigStarHat_all <- get.CI(SigStarHat_data_full, by_net=0)
```


## Accuracy plots

```{r}

plot_code <- path(code.dir, "plot_together.R")
source(plot_code)

```


### Accuracy plots: Mean over all networks

```{r}

vars.to.plot <- c("vegetables",   "eggs",         "meatProducts",    "cheese",       "milkProducts", "poultry")  
CI.lvl <- 0.95

data.in <- rank_data_full 
y.lab.in <- "Rank (out of 6)"
y.lim.in <- c(1, 3)
p_rank_overall <- plot.overall.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, y.lab.in=y.lab.in, y.lim.in=y.lim.in)

data.in <- ACC2_data_full 
y.lab.in <- "Accuracy"
y.lim.in <- c(0.5, 1)
p_ACC_overall <- plot.overall.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, y.lab.in=y.lab.in, y.lim.in=y.lim.in)

data.in <- SigStar_data_full 
y.lab.in <- "Norm-Sig $N^{*}$"
y.lim.in <- c(0.65, 1)
p_SigStar_overall <- plot.overall.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, y.lab.in=y.lab.in, y.lim.in=y.lim.in)

data.in <- SigStarHat_data_full 
y.lab.in <- "Norm-Sig $\\hat{N}$"
y.lim.in <- c(0.65, 1)
p_SigStarHat_overall <- plot.overall.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, y.lab.in=y.lab.in, y.lim.in=y.lim.in)

#(p_rank_overall + p_ACC_overall) / (p_SigStar_overall + p_SigStarHat_overall) + plot_layout(guides = "collect") 


```


## Accuracy plots by network WITHOUT overall

### Create plots

```{r}

## Params for each of the plots
vars.to.plot <- c("vegetables",   "eggs",         "meatProducts",    "cheese",       "milkProducts", "poultry")  
CI.lvl <- 0.5
plot.mean <- 0

data.in <- rank_data_full 
y.lab.in <- "Rank (out of 6)"
y.lim.in <- c(1, 3)
p_rank_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                        y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- ACC2_data_full 
y.lab.in <- "Accuracy"
y.lim.in <- c(0.5, 1)
p_ACC_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                       y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- SigStar_data_full 
y.lab.in <- "Norm-Sig $N^{*}$"
y.lim.in <- c(0.65, 1)
p_SigStar_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                           y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- SigStarHat_data_full 
y.lab.in <- "Norm-Sig $\\hat{N}$"
y.lim.in <- c(0.65, 1)
p_SigStarHat_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                              y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

```

### Print accuracy metric plots for each network next to overall

```{r}

(p_rank_overall + p_rank_together) / (p_ACC_overall + p_ACC_together) / (p_SigStar_overall + p_SigStar_together) / (p_SigStarHat_overall + p_SigStarHat_together) + plot_layout(guides = "collect") 

# pdf(file = path(output.dir, "accuracy/without_mean.pdf"), width=10, height =10)
# 
# (p_rank_overall + p_rank_together) / (p_ACC_overall + p_ACC_together) / (p_SigStar_overall + p_SigStar_together) / (p_SigStarHat_overall + p_SigStarHat_together) + plot_layout(guides = "collect")
# 
# dev.off()

```


## Accuracy plots by network WITH overall

### Create plots

```{r}

## Params for each of the plots
vars.to.plot <- c("vegetables",   "eggs",         "meatProducts",    "cheese",       "milkProducts", "poultry")  
CI.lvl <- 0.95
plot.mean <- 1

data.in <- rank_data_full 
y.lab.in <- "Rank (out of 6)"
y.lim.in <- c(1, 4)
p_rank_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                        y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- ACC2_data_full 
y.lab.in <- "Accuracy" #(rank $N^{*} \\leq 2$)" # Accuracy
y.lim.in <- c(0, 1)
#y.lim.in <- c(0, 1)
p_ACC_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                       y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- SigStar_data_full 
y.lab.in <- "$\\Psi^{norm}_{N^*}$"  #"Norm-Sig $N^{*}$" #"Norm-Sig $N^{*}$"
#y.lim.in <- c(0.65, 1)
y.lim.in <- c(0,1.55)
#y.lim.in <- c(0,.01)
p_SigStar_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                           y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

data.in <- SigStarHat_data_full 
y.lab.in <- "$\\Psi^{norm}_{N^*}$"  #"Norm-Sig $\\hat{N}$" #"Norm-Sig $\\hat{N}$"
#y.lim.in <- c(0.65, 1)
y.lim.in <- c(0,1.55)
#y.lim.in <- c(0,.01)
p_SigStarHat_together <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                              y.lab.in=y.lab.in, y.lim.in=y.lim.in,plot.mean=plot.mean)

p_SigStar_together + p_SigStarHat_together + p_rank_together + p_ACC_together + plot_layout(guides="collect")

```

### Print accuracy metric plots for each network WITH overall

```{r}

#p_rank_together + p_ACC_together + p_SigStar_together + p_SigStarHat_together + plot_layout(guides="collect")

pdf(file = path(output.dir, "accuracy/final/Germany_NormSig_FREE_650ob_CI95.pdf"), width=10, height =10)

p_rank_together + p_ACC_together + p_SigStar_together + p_SigStarHat_together + plot_layout(guides="collect")

dev.off()

```


## SigStarHat - SigStar

```{r}

SigStar_join <- SigStar_data_full
SigStar_join$SigStar <- SigStar_join$value
SigStar_join$value <- NULL

SigStar_join <- cbind(SigStar_join, SigStarHat_data_full$value)
SigStar_join$"SigStarHat" <- SigStar_join[,5]
SigStar_join[,5] <- NULL

SigStar_join$value <- SigStar_join$SigStar / SigStar_join$SigStarHat


vars.to.plot <- c("vegetables",   "eggs",         "meatProducts",    "cheese",       "milkProducts", "poultry")  
CI.lvl <- 0.5
# data.in <- SigStar_join 
# y.lab.in <- "Difference"
# y.lim.in <- c(0, .15)
# p_SigStar_diff <- plot.overall.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, y.lab.in=y.lab.in, y.lim.in=y.lim.in)
# p_SigStar_diff
data.in <- SigStar_join 
y.lab.in <- "Norm-Sig error ($\\hat{N} - N^{*}$)"
y.lim.in <- c(0, 1)
p_SigStar_diff <- plot.together.ribbon(data.in=data.in,vars.to.plot=vars.to.plot,CI.lvl=CI.lvl, 
                                       y.lab.in=y.lab.in, y.lim.in=y.lim.in, plot.mean=1)
p_SigStar_diff

pdf(file = path(output.dir, "accuracy/NormSig_error.pdf"), width=10, height =10)
p_SigStar_diff
dev.off()

```

```{r}

## Source supporting functions
convergence_readin <- path(code.dir, "get_convergence.R")
source(convergence_readin)

## GET MEAN AND CI FOR EACH NETWORK AT INCREASING NUMBERS OF ITERATIONS USING STAT_SUMMARY

nr_ob_convg <- 650 #nr_obIter 

test.iter.idx <- c(seq(10,nr_ob_convg,10))
num.ill.idx <- 300
ACC.data.in <- ACC2_data_full
#ACC.data.in <- rank_data_full
mean.CI.overall.ACC <- get.conv(test.iter.idx=test.iter.idx, num.ill.idx = num.ill.idx, ACC.data.in = ACC.data.in)

# for (i in 1:nrow(mean.CI.overall.ACC)){
#   if (mean.CI.overall.ACC$ymax[i] > 1) mean.CI.overall.ACC$ymax[i] = 1
# }

traj.CI <- mean.CI.overall.ACC
#chart.title <- "Convergence in rank of Norm-Sig"
chart.title <- "Convergence in accuracy of Norm-Sig"
y.lab.in <- "Accuracy"
y.max.in <- 1
plot.conv.ACC <- plot.together.ribbon.conv(traj.CI=traj.CI, y.lab.in=y.lab.in, y.max.in=y.max.in, chart.title=chart.title)
plot.conv.ACC

# pdf(file = path(output.dir, "accuracy/final/conv_NormSigRank_650ob_CI95.pdf"), width=10, height =10)
# plot.conv.ACC
# dev.off()

```


```{r}

## Source supporting functions
convergence_readin <- path(code.dir, "get_convergence.R")
source(convergence_readin)

## GET MEAN AND CI FOR EACH NETWORK AT INCREASING NUMBERS OF ITERATIONS USING STAT_SUMMARY

nr_ob_convg <- 650 #nr_obIter 

test.iter.idx <- c(seq(10,nr_ob_convg,10))
num.ill.idx <- 300
#ACC.data.in <- ACC2_data_full
ACC.data.in <- rank_data_full
mean.CI.overall.ACC <- get.conv(test.iter.idx=test.iter.idx, num.ill.idx = num.ill.idx, ACC.data.in = ACC.data.in)

# for (i in 1:nrow(mean.CI.overall.ACC)){
#   if (mean.CI.overall.ACC$ymax[i] > 1) mean.CI.overall.ACC$ymax[i] = 1
# }

traj.CI <- mean.CI.overall.ACC
chart.title <- "Convergence in rank of Norm-Sig"
#chart.title <- "Convergence in accuracy of Norm-Sig"
y.lab.in <- "Accuracy at 300 illnesses"
y.max.in <- 4
plot.conv.rank <- plot.together.ribbon.conv(traj.CI=traj.CI, y.lab.in=y.lab.in, y.max.in=y.max.in, chart.title=chart.title)


# pdf(file = path(output.dir, "accuracy/final/conv_NormSigRank_650ob_CI95.pdf"), width=10, height =10)
# plot.conv.ACC
# dev.off()

```


```{r}

plot.conv.rank + plot.conv.rank 

```


